Gapfilling the number of farms to add for tuna countries based on tonnes of production

### 2021-05-20 marine/bivalve/bivalve_farms/STEP3_gapfill_biv.Rmd
checked the median global tonnes/farm

avg_global_bivalve_tonnes_per_farm = mean(tonnes_per_farm$tonnes_per_farm)
avg_global_bivalve_tonnes_per_farm # 283.4135
```

>>>>

avg_global_bivalve_tonnes_per_farm = mean(tonnes_per_farm$tonnes_per_farm)
avg_global_bivalve_tonnes_per_farm # 283.4135

med_global_bivalve_tonnes_per_farm <- median(tonnes_per_farm$tonnes_per_farm)
med_global_bivalve_tonnes_per_farm # 134.3808
```

### 2021-05-20 marine/marine_fish_general/finfish_farms/STEP3_gapfill_finfish.Rmd
checked the median global tonnes/farm

avg_global_marine_fish_general_tonnes_per_farm = mean(tonnes_per_farm$tonnes_per_farm)
avg_global_marine_fish_general_tonnes_per_farm # 865.6905
```

>>>>

avg_global_marine_fish_general_tonnes_per_farm = mean(tonnes_per_farm$tonnes_per_farm)
avg_global_marine_fish_general_tonnes_per_farm # 865.6905

med_global_marine_fish_general_tonnes_per_farm = median(tonnes_per_farm$tonnes_per_farm)
med_global_marine_fish_general_tonnes_per_farm # 172.4093
```

### 2021-05-20 marine/salmon/salmon_farms/STEP3_gapfill_salmon.Rmd
made the figures!
checked the median global tonnes/farm

farm_files <- list.files(here("marine/salmon/salmon_farm/data/known_farm_sites_2_4_5"), full=TRUE)
all_known_farms = plyr::ldply(farm_files, read_csv) %>%
  mutate(type = "salmon")

number_files <- list.files(here("marine/salmon/salmon_farm/data/known_number_farms_3"), full=TRUE)
all_number_3 = plyr::ldply(number_files, read_csv)

subset_farms_files <- list.files(here("marine/salmon/salmon_farm/data/subset_known_add_points_4"), full=TRUE)
subset_add_4 = plyr::ldply(subset_farms_files, read_csv)

no_info_files <- list.files(here("marine/salmon/salmon_farm/data/no_info_1"), full=TRUE)
no_info_1 = plyr::ldply(no_info_files, read_csv)

@@

Read in relevant production data
```{r}
salmon_tonnes <- read_csv(here::here("marine/salmon/salmon_farm/data/fao_mariculture_salmon.csv")) %>%
  mutate(type = "salmon") %>%
  filter(year == 2017)
```

@@

avg_global_salmon_tonnes_per_farm = mean(tonnes_per_farm$tonnes_per_farm)
avg_global_salmon_tonnes_per_farm # 930.3976
```

>>>>

farm_files <- list.files(here("marine/salmon/salmon_farms/data/known_farm_sites_2_4_5"), full=TRUE)
all_known_farms = plyr::ldply(farm_files, read_csv) %>%
  mutate(type = "salmon")

number_files <- list.files(here("marine/salmon/salmon_farms/data/known_number_farms_3"), full=TRUE)
all_number_3 = plyr::ldply(number_files, read_csv)

subset_farms_files <- list.files(here("marine/salmon/salmon_farms/data/subset_known_add_points_4"), full=TRUE)
subset_add_4 = plyr::ldply(subset_farms_files, read_csv)

no_info_files <- list.files(here("marine/salmon/salmon_farms/data/no_info_1"), full=TRUE)
no_info_1 = plyr::ldply(no_info_files, read_csv)

@@

Read in relevant production data
```{r}
salmon_tonnes <- read_csv(here::here("marine/salmon/salmon_farms/data/fao_mariculture_salmon.csv")) %>%
  mutate(type = "salmon") %>%
  filter(year == 2017)
```

@@

avg_global_salmon_tonnes_per_farm = mean(tonnes_per_farm$tonnes_per_farm)
avg_global_salmon_tonnes_per_farm # 927.156

med_global_salmon_tonnes_per_farm = median(tonnes_per_farm$tonnes_per_farm)
med_global_salmon_tonnes_per_farm # 520.5484
```

### 2021-05-20 marine/shrimp/shrimp_farms/STEP3_gapfill_shrimp.Rmd
fixed some errors with greece (finfish), australia (bivalve), and belize (shrimp)
checked the median global tonnes/farm

avg_global_shrimp_tonnes_per_farm = mean(tonnes_per_farm$tonnes_per_farm)
avg_global_shrimp_tonnes_per_farm # 337.7357
```

>>>>

avg_global_shrimp_tonnes_per_farm = mean(tonnes_per_farm$tonnes_per_farm)
avg_global_shrimp_tonnes_per_farm # 336.5783

med_global_shrimp_tonnes_per_farm = median(tonnes_per_farm$tonnes_per_farm)
med_global_shrimp_tonnes_per_farm # 174.15
```

### 2021-05-20 marine/tuna/tuna_farms/STEP3_gapfill_tuna.Rmd
checked the median global tonnes/farm

avg_global_tuna_tonnes_per_farm = mean(tonnes_per_farm$tonnes_per_farm)
avg_global_tuna_tonnes_per_farm # 277.4158
```

>>>>

avg_global_tuna_tonnes_per_farm = mean(tonnes_per_farm$tonnes_per_farm)
avg_global_tuna_tonnes_per_farm # 277.4158

med_global_tuna_tonnes_per_farm = median(tonnes_per_farm$tonnes_per_farm)
med_global_tuna_tonnes_per_farm # 172.3696
```
